---
title: 'IS 471: Spring 2018'
subtitle: Homework 3
author: Student Name (STUDENT_ID)
output:
  pdf_document:
    df_print: kable
    fig_caption: yes
    highlight: tango
    number_sections: yes
  word_document: default
---

Please write your code in R and submit your script and results for each of the following. Note that R does not accept 0 as an index for a vector. So every vector starts with 1. 

1.	Find the 8 bit binary number for the following characters: "A", "t", "@", "17", "9", "&" [hint: use binary() in package compositions].
```{r}
# code goes here

```

2.	Find the decimal numbers for the following: "00010110", "00011101", "01011011", "01100101", "00001010", "01100100".
```{r warning=FALSE}
# code goes here

```

3.	For the seed: "MHID9870"
    a)	Create the UTF8 encoding.
    ```{r}
    # code goes here
    
    ```
    b)	Create the 8 bit binary form for the results of a).
    ```{r}
    # code goes here
    
    ```
    c)	Split the strings into individual bits.
    ```{r}
    # code goes here
    
    ```
    d)	Unlist the result of c).
    ```{r}
    # code goes here
    
    ```
    e)	Put the results of d) into one integer vector.
    ```{r}
    # code goes here
    
    
    ```
  
4.	Fill three variables x, y, and z with the results of 3 such that x gets the first 19, y gets the next 22, and z gets the last 23 bits. Initialize an integer vector k of length 128.
    ```{r}
    # code goes here
    
    ```

5.	Find the majority value for x[9], y[11] and z[11]. 
    ```{r}
    # code goes here
    
    ```
6.	Write code for the following: if x steps then shift x to the right by 1 bit. Next assign the appropriate value to x[1]. Do the same for y and z.
    ```{r}
    # code goes here
    
    ```
7.	Create key stream bit by XOR-in the appropriate bits from x, y, and z vectors.
    ```{r}
    # code goes here
    
    ```
8.	Write a function for the above and create a 128 bit key stream with the seed mentioned in question 3. You function should contain two parameters: a seed and a key length.
    ```{r}
    # code goes here
    
    ```
9.	Create an integer vector S with values from 1-5. Swap elements 1 and 4. [Hint: use the swap() function in package seqinr.
    ```{r}
    # code goes here
    
    ```
10.	Implement RC4 for generating key streams. You function should contain two parameters: a seed and a key length.
    ```{r}
    # code goes here
    
    ```
