---
title: 'IS 471: Spring 2018'
subtitle: Homework 4
output:
  word_document: default
  pdf_document:
    df_print: kable
    fig_caption: yes
    highlight: tango
    number_sections: yes
---
```{r global_options, include=FALSE}
# knitr::opts_chunk$set(eval = FALSE, include = FALSE)
```

Please write your code in R and submit your script and results for each of the following. 

1.	Store the following binary number as a character string s: "110011".  (10 points)
```{r message=FALSE, warning=FALSE}
library(seqinr)
library(compositions)
s = "110011"
```
2.	Convert this into a character vector v. (10 points)
```{r}
v = unlist(strsplit(s, "")) # "1" "1" "0" "0" "1" "1"
```
3.	Expand the character vector v to 8 bits as follows: swap v[3] and v[4] . (10 points)
```{r}
swap(v[3], v[4]) # 
v = unlist(strsplit(s, "")) # "1" "1" "0" "0" "1" "1"
```
4.	Replicate v[3] and v[4] .  The result (call it ev) should be a character vector of size 8. (10 points)
```{r}
ev = vector(mode="character", length = 8)
ev = append(v[1:6], v[3:4], after = 2) # # "1" "1" "0" "0" "0" "0" "1" "1"
```
5.	Write a function called expand() that takes a binary vector of size 6 as input and returns a binary vector of size 8 as output. (20 points)
```{r}
expand = function(binaryVec){
  
  v = unlist(strsplit(binaryVec, ""))
  swap(v[3], v[4])
  ev = vector(mode="character", length = 8)
  ev = append(v[1:6], v[3:4], after = 2)
  return(ev)
}
expand("123456") # "1" "2" "4" "3" "4" "3" "5" "6"
```
6.	Create two character vectors S11 and S12 such that S11 contains the binary representations of the numbers (5,2,1,6,3,4,7,0), and S12 contains those of the numbers (1,4,6,2,0,7,5,3). (10 points)
```{r}
numbers = c(5,2,1,6,3,4,7,0)
s11=binary(numbers) # [1] "101" "010" "001" "110" "011" "100" "111" "000"

numbers2 = c(1,4,6,2,0,7,5,3)
s12=binary(numbers2) # [1] "001" "100" "110" "010" "000" "111" "101" "011"
```
7.	Let b="1101". Extract the last three characters. Convert the last three characters into decimal and store it in a variable called tempVal.  Write an "if-then-else" statement such that if b[1] == 0 retrieve the value of S11[tempval]. If b[1]==1  retrieve the value of S12[tempval]  and store it in a variable tempRet. (10 points)
```{r message=FALSE, warning=FALSE}
b=unlist(strsplit("1101", ""))
tempVal=b
tempVal=c(tempVal[2:4])
tempVal=paste(tempVal[1:3])
tempVal=toString(c(tempVal[1], tempVal[2], tempVal[3]))
tempVal=gsub(pattern = ", ", replacement = "", x = tempVal, fixed = TRUE)
tempVal=strtoi(tempVal, base=2)

if (b[1]==0) {
  tempRet= s11[tempVal+1]
} else {
  tempRet= s12[tempVal+1]
}
#111
```
8.	Write a function called S11_function that takes a block of 4-character binary (such as "1110") and, using the two s-boxes from question 6, returns a 3-character binary number using the logic that if the first character is "0" then use S11, otherwise use S12.  (20 points)
```{r message=FALSE, warning=FALSE}
s11_function = function(binary_val){
  b=unlist(strsplit(binary_val, ""))
  tempVal=b
  tempVal=c(tempVal[2:4])
  tempVal=paste(tempVal[1:3])
  tempVal=toString(c(tempVal[1], tempVal[2], tempVal[3]))
  tempVal=gsub(pattern = ", ", replacement = "", x = tempVal, fixed = TRUE)
  tempVal=strtoi(tempVal, base=2)
  
  if (b[1]==0) {
    tempRet= s11[tempVal+1]
  } else {
    tempRet= s12[tempVal+1]
  }
  
  return(tempRet)
}
s11_function("1000") #001
```