---
title: 'IS 471: Spring 2018'
subtitle: Homework 9
# author: Andrew Peterson (NA75257)
output:
  pdf_document:
    df_print: kable
    fig_caption: yes
    highlight: tango
    number_sections: yes
  word_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(openssl)
```



Background
==========

Secure Hash Algorithm 1
-----------------------

use `sha1()` function from `openssl` library to calculate the SHA-1 hash of a value

Reading a CSV file
------------------

Use `read.csv()` function to read a CSV file to a data-frame


R DataFrame
-----------

A data frame is a table or a two-dimensional array-like structure in which each column contains values of one variable and each row contains one set of values from each column.

Following are the characteristics of a data frame.

* The column names should be non-empty.
* The row names should be unique.
* The data stored in a data frame can be of numeric, factor or character type.
* Each column should contain same number of data items.


Here is an example of a built in data-frame. I'm using `head()` to read the first few values of the data-frames
```{r}
head(mtcars)
```

### Indexing in Dataframe

Here is the cell value from the first row, second column of mtcars.

```{r}
mtcars[1, 2] 
```

Moreover, we can use the row and column names instead of the numeric coordinates.

```{r}
mtcars["Mazda RX4", "cyl"] 
```

Lastly, the number of data rows in the data frame is given by the nrow function.

```{r}
nrow(mtcars)    # number of data rows 
```

And the number of columns of a data frame is given by the ncol function.

```{r}
ncol(mtcars)    # number of columns 
```


Questions
=========
Please write your code in the given **.Rmd** file and submit your script. Submitting screenshot or just only PDF/DOC file will result in an automatic penalty.


**Question 1** (15 Points)

Suppose that Alice, Bob, and Charlie are bidding for a camera. The estimated cost of the camera is between \$500-\$550. Each bidder first submits the hashed value of their bid with SHA-1. Assuming that the hash values for Alice and Bob are `ce09b127d48f83868a45645e246d3b52f4bdecbe` and `10d293a95915109e7675b011f404213902624f14` respectively, what is the minimum amount that Charlie needs to bid to win?

```{r}
i = 500
alice_bid = 'ce09b127d48f83868a45645e246d3b52f4bdecbe'
bob_bid = '10d293a95915109e7675b011f404213902624f14'
dollar_amount = 500
dollar_amount2 = 500
min_bid = 500
while (i <= 550){
  dollar = toString(i)
  hashed_dollar = sha1(dollar)

  if (hashed_dollar == alice_bid){
    i = 551
  }
  i = i + 1
  dollar_amount = dollar_amount + 1
}

i = 500

while (i <= 550){
  dollar = toString(i)
  hashed_dollar = sha1(dollar)

  if (hashed_dollar == bob_bid){
    i = 551
  }
  i = i + 1
  dollar_amount2 = dollar_amount2 + 1
}

print(dollar_amount)
print(dollar_amount2)

if (dollar_amount >= dollar_amount2){
  min_bid = dollar_amount + 1
} else {
  min_bid = dollar_amount2 + 1
}
print(min_bid)

```
**Question 2** (10 Points)

Read the password file `hashed_passwords.csv` into a data-frame `df`. Read the dictionary `trudy_pass.csv` into a data-frame called `trudy.df`. Examine the content of the data-frames with `head()`.

```{r}
df = read.csv('hashed_passwords.csv')
trudy.df = read.csv('trudy_pass.csv')

head_df = head(df)
head_trudy.df = head(trudy.df)
print(head_df)
print(head_trudy.df)
```

**Question 3** (10 Points)

Calculate the hashes for each row in `trudy.df` by combining the password and salt. Use `paste0` for combining. Save them in a vector called `hashes`.

```{r}
hashes = paste0(trudy.df[[2]], trudy.df[[1]])
hashes = sha1(hashes)

```


**Question 4** (15 Points)

Find all passwords in Trudy's dictionary that also appears in the hashed password file. You will need to use `for` loop to achieve this. (Hint: you should get 300 matches)
```{r}
```